# Exercise Solutions {#exercise-solutions}

```{r, eval = TRUE, echo = FALSE}
river_means <- function(data, pattern) {
  desired_rivers <- grep(pattern, names(data))
  new_data <- data[, desired_rivers]
  rowMeans(new_data)
}
```

## Building an R Package {-}

**Exercise 1.1.1.1** ([internal link](#ex-set1)) 
What are some of your favorite R packages?

Answer 1.1.1.1
This is for you to answer! I have many favorites, but a few are devtools, purrr, rlang, rticles, styler, and usethis.

**Exercise 1.1.1.2** ([internal link](#ex-set1)) 
Of those we have talked about so far, what benefits of R packages are most appealing to you?

Answer 1.1.1.2 
This is for you to answer! One of the the most appealing benefits to me is the structure that helps keep me organized.

**Exercise 1.2.4.1.1** ([internal link](#ex-set2)) 
How many functions does `river_means()` call within the body of the function? What package are these functions in?

Answer 1.2.4.1.1 
There are five functions: `<-`, `grep()`, `names()`, `[`, and `rowMeans()`. They are all in the "base" package -- this fact be can seen in each function's documentation
```{r}
?`<-`
?grep
?names
?`[`
?rowMeans
```

**Exercise 1.2.4.1.2** ([internal link](#ex-set2)) 
Try using `river_means()` with a few different patterns. Do you notice anything strange?

Answer 1.2.4.1.1 
Strange behavior occurs when the pattern matches only one river or zero rivers. If the pattern matches only one river, there is an error:
```{r, eval = TRUE}
river_means(river, "R")
```

If the pattern matches zero rivers, the mean is `NaN` (which stands for not a number)
```{r, eval = TRUE}
river_means(river, "ZZZ")
```

These are both unintended and are discussed more in Debugging ([internal link](#debugging)).

**Exercise 1.2.7.1.1** ([internal link](#ex-set3)) 
Write a new function, `river_stats()`, that takes a data frame, pattern, and a general function by which to summarize river length and discharge. This general function should not be an actual function but rather a placeholder for a function a user inserts themselves.

Answer 1.2.7.1.1
```{r, eval = TRUE}
#' Summary statistics of river lengths and discharges
#'
#' @param data A data frame with two rows. The first row indicates river length and
#'   second row indicates river discharge. The columns of data indicate river names.
#' @param pattern A pattern by which to include only particular rivers
#' @param FUN A function to summarize the rivers
#'
#' @return The summarized river length and mean river discharge for the desired rivers
#' @export
#'
#' @examples
#' data("river")
#' river_stat(river, "Mi", min)
river_stats <- function(data, pattern, FUN) {
  desired_rivers <- grep(pattern, names(data))
  new_data <- data[, desired_rivers]
  apply(new_data, 1, FUN)
}
river_stats(river, "Mi", min)
river_stats(river, "Mi", max)
river_stats(river, "Mi", mean)
river_stats(river, "Mi", stats::median)
```

**Exercise 1.2.7.1.2** [internal link](#ex-set3)) 
Rewrite `river_stats()` from the previous exercise so that `river_stats()` also takes additional arguments to the summarizing function (hint: use `...` as an argument)

Answer 1.2.7.1.2
```{r, eval = TRUE}
#' Summary statistics of river lengths and discharges
#'
#' @param data A data frame with two rows. The first row indicates river length and
#'   second row indicates river discharge. The columns of data indicate river names.
#' @param pattern A pattern by which to include only particular rivers
#' @param FUN A function to summarize the rivers
#' @param ... Additional arguments to pass to \code{FUN}
#'
#' @return The summarized river length and mean river discharge for the desired rivers
#' @export
#'
#' @examples
#' data("river")
#' river_stat(river, "Mi|C", mean, trim = 0.5)
river_stats <- function(data, pattern, FUN, ...) {
  desired_rivers <- grep(pattern, names(data))
  new_data <- data[, desired_rivers]
  apply(new_data, 1, FUN, ...)
}
river_stats(river, "Mi|C", mean, trim = 0)
river_stats(river, "Mi|C", mean, trim = 0.5)
```

**Exercise 1.2.10.1** ([internal link](#ex-set4)) 
Write similar tests for `river_means()` (discharge), `river_medians()` (length), and `river_medians()` (discharge).

Answer 1.2.10.1 
```{r, eval = TRUE}
testthat::test_that("the mean discharge is calculated correctly in a test case", {
  
  # calculate values required for the test for discharge

  ## calculate the means from the function
  river_means_val <- river_means(river, "Missouri|Mississippi")
  river_means_discharge <- river_means_val[[2]]

  ## calculate the means "by hand"
  raw_vec_discharge <- unlist(river["discharge", c("Missouri", "Mississippi")])
  raw_means_discharge <- mean(raw_vec_discharge)
  
  # perform the actual test for discharge

  ## check that the function and "by hand" output matches
  expect_equal(river_means_discharge, raw_means_discharge)
})
```

```{r, eval = TRUE}
testthat::test_that("the median length is calculated correctly in a test case", {
  
  # calculate values required for the test for length

  ## calculate the medians from the function
  river_medians_val <- river_medians(river, "Missouri|Mississippi")
  river_medians_length <- river_medians_val[[1]]

  ## calculate the medians "by hand"
  raw_vec_length <- unlist(river["length", c("Missouri", "Mississippi")])
  raw_medians_length <- median(raw_vec_length)
  
  # perform the actual test for length

  ## check that the function and "by hand" output matches
  expect_equal(river_medians_length, raw_medians_length)
})
```

```{r, eval = TRUE}
testthat::test_that("the mean discharge is calculated correctly in a test case", {
  
  # calculate values required for the test for discharge

  ## calculate the medians from the function
  river_medians_val <- river_medians(river, "Missouri|Mississippi")
  river_medians_discharge <- river_medians_val[[2]]

  ## calculate the medians "by hand"
  raw_vec_discharge <- unlist(river["discharge", c("Missouri", "Mississippi")])
  raw_medians_discharge <- median(raw_vec_discharge)
  
  # perform the actual test for discharge

  ## check that the function and "by hand" output matches
  expect_equal(river_medians_discharge, raw_medians_discharge)
})
```

**Exercise 1.2.10.2** ([internal link](#ex-set4)) 
Check out the covr ([external link](https://cran.r-project.org/web/packages/covr/vignettes/how_it_works.html)) package, which quantifies how much of your package's code is used by your tests.

Answer 1.2.10.2
NA

**Exercise 1.2.14.1.1** ([internal link](#ex-set5))
Find the argument to `devtools::install()` that identifies whether vignettes are built alongside installation. What is the default value of this argument?

Answer 1.2.14.1.1
Running 
```{r}
?devtools_install
```
we see that `build_vignettes` controls whether vignettes are build alongside installation. The default argument for `build_vignettes` is `FALSE`.



**Exercise 1.3.4.1.1** ([internal link](#ex-set6))
Rewrite `river_medians()` so that it stops and returns an informative error message when the pattern matches zero rivers.

Answer 1.3.4.1.1
```{r, eval = TRUE}
river_medians <- function(data, pattern) {
  desired_rivers <- grep(pattern, names(data))
  if (length(desired_rivers) == 0) {
    stop("The pattern provided does not match any rivers in the data provided.")
  }
  new_data <- data[, desired_rivers, drop = FALSE]
  rowMeans(new_data)
}
river_medians(rivers, "ZZZ")
```

The error messages in the `RPRW` package are more informative but more difficult to code.

## Making an R Package a Research Compendium {-}

**Exercise 2.1.1.1** ([internal link](#ex-set7))
What principles of a research compendium seem most beneficial to you?

Answer 2.1.1.1
This is for you to answer! To me, the file organization, file separation, and computational details all seem like wonderful principles!

**Exercise 2.2.1.1** ([internal link](#ex-set8))
Can you identify any benefits to a research compendium that are not already on this list?

Answer 2.2.1.1
This is for you to answer! To me, another benefit is leveraging a structure that facilitates reproducibility.

**Exercise 2.4.1.1** ([internal link](#ex-set9))
There is a folder name within `inst` that should be avoided -- what is it?

Answer 2.4.1.1
You should not name a folder in `inst` named `doc`. The package building process automatically creates a folder named `doc` upon installation -- so putting a `doc` folder in `inst` creates conflicts. For those that use GitHub, `inst/doc` is automatically placed in `gitignore`.

**Exercise 2.6.1.1** ([internal link](#ex-set10))
Run `?devtools::build` to look at some additional arguments -- which seem useful to you?

Answer 2.6.1.1
This is for you to answer! But `vignettes` and `manual` seem important to be aware of.

## Extensions {-}

**Exercise 3.1.1.1** ([internal link](#ex-set11))
What are some drawbacks of running `setwd()` whenever you want to set a working directory?

Answer 3.1.1.1
* You have to remember to run `setwd()` anytime you want to re-run a script
* It is easy to run `setwd()` and point to the wrong working directory
* It means that your code is harder to share because someone else will have to change the line of code calling `setwd()`
* Can you think of more?

**Exercise 3.1.1.2** ([internal link](#ex-set11))
Look into the here ([external link](https://here.r-lib.org/)) package, designed to help solve working directory problems (that can even occur within R Projects).

Answer 3.1.1.1
NA

**Exercise 3.2.1.1** ([internal link](#ex-set12))
What benefits do you see to R Markdown documents?

Answer 3.1.1.1
This is for you to answer! One of my favorite benefits is making reproducible figures, tables, and output within the document.

**Exercise 3.2.1.2** ([internal link](#ex-set12))
Save the basic R Markdown template we just discussed and knit it to see its contents.

Answer 3.1.1.1
Go to "File -> New File -> R Markdown" and create an R Markdown template. Then in the editor (upper-left) window, click "Knit". Save the file to a location and then the document will knit to an HTML document and pop up in a default viewer. To knit to other output types, click on the down arrow to the right of the "Knit" button.


**Exercise 3.3.1.1** ([internal link](#ex-set13))
Visit this ([external](https://github.com/rstudio/rticles)) to see all the journals that rticles has a template for.

Answer 3.1.1.1
NA

**Exercise 3.7.1.1** ([internal link](#ex-set14))
1. A data set is called "tidy" if it has three qualities: 1) each variable has its own column, 2) each observation has its own row, and 3) each value has its own cell. Is `river` tidy?

Answer 3.7.1.1
`river` is not tidy. The river names are spread across columns. One could also argue that `length` and `discharge` are both values of a `metric` argument. Then a tidy `river` data set would look like

```{r, eval = TRUE, echo = FALSE}
library(tibble)
library(tidyr)
library(dplyr)
river_tidy <- river %>%
  tibble::rownames_to_column(var = "metric") %>% 
  tidyr::pivot_longer(Missouri:Canadian) %>%
  dplyr::select(name, metric, value)
```


```{r, eval = TRUE}
river_tidy
```

**Exercise 3.7.1.2** ([internal link](#ex-set14))
Make `river` tidy

Answer 3.7.1.1
```{r}
# approach 1 to loading packages
library(tibble) # run install.packages("tibble") if needed
library(tidyr) # run install.packages("tidyr") if needed
library(dplyr) # # run install.packages("dplyr) if needed
```

```{r}
# approach 2 to loading packages
library(tidyverse) # run install.packages("tidyverse") if needed
```

```{r}
river_tidy <- river %>%
  tibble::rownames_to_column(var = "metric") %>% 
  tidyr::pivot_longer(Missouri:Canadian) %>%
  dplyr::select(name, metric, value)
```

```{r, eval = TRUE}
river_tidy
```

